---
title: "cleaningdata"
author: "Youngjoon Kim"
date: "2/14/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. load raw data

```{r, echo=FALSE}
library(readr)
setwd("~/BA888/meetups-data-from-meetupcom")
category = read_csv("categories.csv")
city = read_csv("cities.csv")
event = read_csv("events.csv")
group = read_csv("groups.csv")
gt = read_csv("groups_topics.csv")
member = read_csv("members.csv")
mt = read_csv("members_topics.csv")
topic = read_csv("topics.csv")
venue = read_csv("venues.csv")
```

### 2. data cleaning
1. each dataset should delete some redundant or unnecessary columns.
2. each 1st cleaned dataset should take care of missing 
3. some strings to be lowered without special character. Time should be unified (to be determined / this was not done yet.)
4. function for removing rows that have any missing data(NA). You can use this function. 
```{r}
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```

5. lets clean raw data in a way of 1st and 2nd stage
```{r}
category_c1 = category %>% select(category_id, category_name)

city_c1 = city %>% select(-country, -localized_country_name)

event_c1 = event %>% select(-event_url, -fee.description, -fee.label, -group.urlname, -headcount, -maybe_rsvp_count,-photo_url, -rating.average, -rating.count, -event_status, -venue.address_2,-venue.country,-venue.localized_country_name,-venue.phone,-venue.repinned,-venue.zip,-visibility,-waitlist_count,-why)
event_c1=completeFun(event_c1, c("description", "event_name"))
event_c1 = event_c1 %>% 
  mutate(duration = duration/3600) %>%
  mutate(utc_offset = utc_offset/3600)

group_c1 = group %>% select(-category.shortname,-country,-group_photo.base_url,-group_photo.highres_link,-group_photo.photo_id,-group_photo.photo_link,-group_photo.thumb_link,-group_photo.type,-link,-organizer.photo.base_url,organizer.photo.highres_link,-organizer.photo.photo_id, -organizer.photo.photo_link,-organizer.photo.thumb_link,-organizer.photo.type,-utc_offset)
group_c1=completeFun(group_c1, c("description", "group_name", "organizer.name", "who", "urlname"))

gt_c1 = gt %>% select(-topic_name)

member_c1 = member %>% select(-country, -link, -member_status)
member_c1=completeFun(member_c1, c("bio", "hometown", "member_name"))

mt_c1 = mt %>% select(-topic_key)

topic_c1 = topic %>% select(-link,-urlkey)

venue_c1 = venue %>% select(-country, -distance, -localized_country_name)
venue_c1=completeFun(venue_c1, c("address_1", "venue_name"))

```

Now we have cleaned raw data except for strings unification. 


