---
title: "Group recommendation"
author: "Youngjoon Kim"
date: "4/30/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1. Top 3 Groups prediction When user choose 'social media' as topic
```{r}
#1. social media  -> new tech
gt_c1 %>% filter(topic_key == 'newtech') %>% select(group_id) -> newtech

newtech1 = inner_join(group_c1, newtech) 


newtech1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3)-> newtech_ny

newtech1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> newtech_il

newtech1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> newtech_ca

newtech_ny
newtech_il
newtech_ca

```

# 2. Top 3 Groups prediction When user choose 'technology' as topic
```{r}
#2.technology -> newtech
newtech_ny
newtech_il
newtech_ca

```

# 3. Top 3 Groups prediction When user choose 'recreational-sports' as topic
```{r}
#3 recreational-sports -> sports
gt_c1 %>% filter(topic_key == 'sports') %>% select(group_id) -> sports

sports1 = inner_join(group_c1, sports) 


sports1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> sports_ny

sports1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> sports_il

sports1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> sports_ca

sports_ny
sports_il
sports_ca

```

# 4. Top 3 Groups prediction When user choose 'recreational-sports' as topic
```{r}
#4 recreational-sports -> outdoors
gt_c1 %>% filter(topic_key == 'outdoors') %>% select(group_id) -> outdoors

outdoors1 = inner_join(group_c1, outdoors) 


outdoors1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> outdoors_ny

outdoors1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> outdoors_il

outdoors1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> outdoors_ca

outdoors_ny
outdoors_il
outdoors_ca

```

# 5. Top 3 Groups prediction When user choose 'culture-exchange' as topic
```{r}
#5 culture-exchange -> language
gt_c1 %>% filter(topic_key == 'language') %>% select(group_id) -> language

language1 = inner_join(group_c1, language) 


language1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> language_ny

language1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> language_il

language1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> language_ca

language_ny
language_il
language_ca
```

# 6. Top 3 Groups prediction When user choose 'mobile-technology' as topic
```{r}
#6 mobile-technology -> newtech
newtech_ny
newtech_il
newtech_ca
```

# 7. Top 3 Groups prediction When user choose 'digcam' as topic
```{r}
#7 digcam -> photo
gt_c1 %>% filter(topic_key == 'photo') %>% select(group_id) -> photo

photo1 = inner_join(group_c1, photo) 


photo1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> photo_ny

photo1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> photo_il

photo1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> photo_ca

photo_ny
photo_il
photo_ca

```

# 8. Top 3 Groups prediction When user choose 'web' as topic
```{r}
#8 web -> newtech
newtech_ny
newtech_il
newtech_ca
```

# 9. Top 3 Groups prediction When user choose 'outdoor-fitness' as topic
```{r}
#9 outdoor-fitness -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 10. Top 3 Groups prediction When user choose 'outdoor-adventures' as topic
```{r}
#10 outdoor-adventures -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 11. Top 3 Groups prediction When user choose 'social-dancing' as topic
```{r}
#11 social-dancing -> dance-lessons
gt_c1 %>% filter(topic_key == 'dance-lessons') %>% select(group_id) -> dance_lessons

dance_lessons1 = inner_join(group_c1, dance_lessons) 


dance_lessons1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> dance_lessons_ny

dance_lessons1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> dance_lessons_il

dance_lessons1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> dance_lessons_ca

dance_lessons_ny
dance_lessons_il
dance_lessons_ca
```

# 12. Top 3 Groups prediction When user choose 'dance-lessons' as topic
```{r}
#12 dance-lessons -> social-dancing
gt_c1 %>% filter(topic_key == 'social-dancing') %>% select(group_id) -> social_dancing

social_dancing1 = inner_join(group_c1, social_dancing) 


social_dancing1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> social_dancing_ny

social_dancing1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> social_dancing_il

social_dancing1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> social_dancing_ca

social_dancing_ny
social_dancing_il
social_dancing_ca
```

# 13. Top 3 Groups prediction When user choose 'sports' as topic
```{r}
#13 sports -> outdoors
outdoors_ny
outdoors_il
outdoors_ca

```

# 14. Top 3 Groups prediction When user choose 'performing-arts' as topic
```{r}
#14 performing-arts -> art
gt_c1 %>% filter(topic_key == 'art') %>% select(group_id) -> art

art1 = inner_join(group_c1, art) 


art1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> art_ny

art1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> art_il

art1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> art_ca

art_ny
art_il
art_ca
```

# 15. Top 3 Groups prediction When user choose 'mobile-technology & technology' as topic
```{r}
#15 mobile-technology,technology - > newtech
newtech_ny
newtech_il
newtech_ca
```

# 16. Top 3 Groups prediction When user choose 'newtech & technology' as topic
```{r}
#16 newtech,technology -> mobile-technology
gt_c1 %>% filter(topic_key == 'mobile-technology') %>% select(group_id) -> mobile_technology

mobile_technology1 = inner_join(group_c1, mobile_technology) 


mobile_technology1 %>% 
  filter(state=='NY') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> mobile_technology_ny

mobile_technology1 %>% 
  filter(state=='IL') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> mobile_technology_il

mobile_technology1 %>% 
  filter(state=='CA') %>% 
  filter(rating  > 4.8) %>% 
  arrange(desc(members)) %>% 
  select(group_name, members) %>% 
  head(3) -> mobile_technology_ca

mobile_technology_ny
mobile_technology_il
mobile_technology_ca
```

# 17. Top 3 Groups prediction When user choose 'sports & wellness ' as topic
```{r}
#17 sports,wellness -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 18. Top 3 Groups prediction When user choose 'music & sports' as topic
```{r}
#18 music,sports -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 19. Top 3 Groups prediction When user choose 'art & sports' as topic
```{r}
#19 art,sports -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 20. Top 3 Groups prediction When user choose 'music & performing-arts' as topic
```{r}
#20 music,performing-arts -> art
art_ny
art_il
art_ca
```

# 21. Top 3 Groups prediction When user choose 'movies & performing-arts' as topic
```{r}
#21 movies,performing-arts -> art
art_ny
art_il
art_ca
```

# 22. Top 3 Groups prediction When user choose 'outdoors & performing-arts' as topic
```{r}
#22 outdoors,performing-arts -> art
art_ny
art_il
art_ca
```

# 23. Top 3 Groups prediction When user choose 'movies & wine' as topic
```{r}
#23 movies, wine -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 24. Top 3 Groups prediction When user choose 'art & wine' as topic
```{r}
#24 art,wine -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 25. Top 3 Groups prediction When user choose 'movies & music' as topic
```{r}
#25 movies, music -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 26. Top 3 Groups prediction When user choose 'art & music' as topic
```{r}
#26 art, music -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

# 27. Top 3 Groups prediction When user choose 'art & movies' as topic
```{r}
#27 art, movies -> outdoors
outdoors_ny
outdoors_il
outdoors_ca
```

