---
title: "Map of Distribution of Top 5 Categories among 3 States"
author: "Andy Kim, Mandi Zhu, Jiaying Hu, Hui Jiang, Zhen Li, Jingxuan Ma"
output: html_document
---

# Data
Kaggle: https://www.kaggle.com/sirpunch/meetups-data-from-meetupcom

# Packages
```{r}
options(digits = 10)
library(dplyr)
library(knitr)
library(plotly)
library(shiny)
library(leaflet)
```

# Load Raw Data & Keep Variables We Need
```{r}
raw_group <- read.csv(file = 'Downloads/BA888/meetups-data-from-meetupcom/groups.csv')
group_category <- raw_group %>% select(category.shortname, lat, lon) %>% filter(category.shortname %in% c('tech', 'socializing', 'career-business', 'outdoors-adventure', 'language')) %>% group_by(category.shortname)
group_category$location <- ifelse(group_category$category.shortname == 'tech', '#ed1c40',
                                  ifelse(group_category$category.shortname == 'socializing', 'yellow', 
                                         ifelse(group_category$category.shortname == 'career-business', 'blue',
                                                ifelse(group_category$category.shortname == 'outdoors-adventure', 'green',
                                                         ifelse(group_category$category.shortname == 'language', 'purple', 'black')))))
```

# Limitation of the data
```{r}
kable(group_category)
```
As you can see the chart above, different groups with different categories have the same longitude and latitude since Meetup protect the user's privacy. Therefore, the are some overlap point when we make the map of distribution of groups.

# Creating the map with leaflet
```{r}
leaflet() %>%
 addTiles() %>%
 addCircleMarkers(group_category$lon,
                  group_category$lat,
                  color = group_category$location,
                  radius = 0.5,
                  fill = T,
                  fillOpacity = 0.2,
                  opacity = 0.6,
                  popup = paste(group_category$category.shortname,group_category$lat,group_category$lon,sep = "")) %>%
 addLegend("topright",
           colors = c("#ed1c40","yellow", "blue", "green", "purple"),
           labels = c("Tech",
                      "Socializing",
                      "Career-business",
                      "Outdoors-Adventure",
                      "Language"),
           opacity = 2.0)
```

Even though there are some overlaping with the points, we can observe that the color of the point more closer to the color of group's categories which means in this area this kind category of groups is more popular. From the graph, the Downtown of New York City has more business-career groups than Uptown of New York City. There are more groups with categories of Socializing and Outdoor-Adventure in the uptown of New York City. In Chichago, more Career-Business locate at the Downtown. And more socializing group locate at suburb.In San Francisco, there are more Tech groups comparing to Chichago and New York since there are lots of tech company located at San Francisco.

# Map with RShiny- Illinois Distribution (Need to have the accurate lon and lat data from Meetup)
```{r}
chi_category <- raw_group %>% filter(state == 'IL')

vars <- c(
  'tech' = 'tech',
  'socializing' = 'socializing',
  'career-business' = 'career-business',
  'outdoors-adventure' = 'outdoors-adventure',
  'language' = 'language'
)

ui <-  fluidPage( 
  leafletOutput(outputId = "mymap"),
  titlePanel("Distribution of five categories among the 3 states"),
  sidebarLayout(
    sidebarPanel(
      selectInput('category', label  = 'Category', vars)),
    mainPanel(
      plotOutput("plot"))
  )
)


server <- function(input,output, session) {
  
  data <- reactive({
    data_input <- chi_category %>% 
      filter(category.shortname == input$category)
  })
  
  
  output$mymap <- renderLeaflet({
    leaflet(df <- data()) %>%
      addTiles() %>%
      addCircleMarkers(chi_category$lon,
                       chi_category$lat,
                       color = 'green',
                       radius = 0.5,
                       fill = T,
                       fillOpacity = 0.2,
                       opacity = 0.6,
                       popup = paste(chi_category$category.shortname,chi_category$lat,chi_category$lon,sep = "")) %>%
      addLegend("topright",
                colors = 'green',
                labels = input$category,
                opacity = 2.0)
  })
}

shinyApp(ui = ui, server = server)
```
Even though we know there is overlaping with the points, we do the RShiny of map of distribution of top five categories in IN. Just in case if we can have the accurate data of groups' longitude and latitude.
