---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE}
library(readr)
library(skimr)
library(ggplot2)
library(tidyverse)
library(stringr)
library(data.table)
library(lubridate)
options(scipen=999, digits = 22)
```


```{r}
event=read_csv('events.csv')
group_topics=read_csv('groups_topics.csv')
group=read_csv('Meetup/meetups-data-from-meetupcom/groups.csv')
member=read_csv('Meetup/meetups-data-from-meetupcom/members.csv')
```

# "Event" visualization 

## Fee-required events versus free events in different activity topics
```{r}
eventFee_topics<-merge(event,group_topics,by='group_id')
eventFee_topics<-eventFee_topics %>% select('event_id','created','fee.required','group_id','topic_id','topic_name')
colSums(is.na(eventFee_topics)==1) #no missing value
eventFee_topics %>% group_by(topic_id,topic_name) %>% count() %>% arrange(topic_id) #topic_name and topic_id is unique matching
eventFee_topics %>% group_by(topic_name) %>% 
  mutate(charged_events=sum(fee.required),total_events=n(),charged_event_ratio=charged_events/total_events) -> eventFee_topics
eventFee_topics %>% mutate(created_year=year(created),charged_event_ratio=round(charged_event_ratio,2))-> eventFee_topics
View(eventFee_topics)
eventFee_topics %>% group_by(topic_name,created_year) %>% 
  summarise(sum_charged=sum(charged_events),sum_total=sum(total_events)) -> eventFee_topics
write_csv(eventFee_topics,'eventFee_topics.csv')
```

## Fee-required events versus free events in different activity catagories
```{r}
eventFee_categories<-merge(event,group,by='group_id')
eventFee_categories<-eventFee_categories %>% select('event_id','created.x','fee.required','group_id','category_id','category.name')
colSums(is.na(eventFee_categories)==1)
eventFee_categories %>% group_by(category_id) %>% 
  mutate(charged_events=sum(fee.required),total_events=n(),charged_event_ratio=charged_events/total_events) -> eventFee_categories
eventFee_categories %>% mutate(created_year=year(created.x),charged_event_ratio=round(charged_event_ratio,2))-> eventFee_categories
View(eventFee_categories)
eventFee_categories %>% group_by(category.name,created_year) %>% 
  summarise(sum_charged=sum(charged_events),sum_total=sum(total_events)) -> eventFee_categories
write_csv(eventFee_categories,'eventFee_categories.csv')
```
## For all fee-required events, average fee each group type 
```{r}
event %>% filter(fee.required==1) %>% group_by(group.name) %>% summarise(avg_fee=mean(fee.amount)) %>% arrange(desc(avg_fee))
```
## Number of event in each Venue (lon and lat)-->Tableau

# "Group" visualization 
## Create time: No.of group created each year
```{r}
group %>% mutate(created_year=year(created))->group
#write_csv(group,'group.csv')
```

## Lat nad lon: number of groups geographically --> Tableau

## Rating: average rating for every category --> Tableau

```{r}

group %>% group_by(created_year) %>% summarise(mean(rating,na.rm = T))  #abnormal low avg rating in 2016 and 2017
group %>% filter(created_year==2017) %>% select(rating) # a lot of 0 value in rating in 2016 and 2017
group %>% mutate(rating=ifelse(rating==0,NA,rating)) ->group
#write_csv(group,'group.csv')
```

# "Member" visualization 
## Average (visit-join) time
```{r}
member$joined=substr(member$joined,1,str_locate(member$joined,' ')[1])
member$visited=substr(member$visited,1,str_locate(member$visited,' ')[1])
member %>% mutate(joined=as.Date(joined,'%m/%d/%y'),visited=as.Date(visited,'%m/%d/%y'))->member
member %>% mutate(time_to_action=visited-joined)->member
mean(member$time_to_action)
```

## Number of groups each member joins (group by member_id)
```{r}
n_group=member %>% group_by(member_id) %>% count() 
member=merge(member,n_group,by='member_id')
colnames(member)[16]<-"n_group"

```

## New member in Meetup every year (earliest ‘join’ time)

```{r}
member$join_year=year(member$joined)
member=member %>% group_by(member_id) %>% mutate(cohort=min(join_year))
table(member$cohort)
#write_csv(member,'member.csv')
```

## Member retention: group by user id and join time(year)
```{r}
with(member,table(cohort,join_year))
```

```{r}
```